---
title: "Anna tutorial week 3"
author: "Anna Li"
date: "1/22/2022"
output: pdf_document
---

```{r}
### Preamble ###
#Purpose:Provide a glimpse at Toronto's marriage license registration situation.
#Author: Anna Li
#Email:annadl.li@mail.utoronto.ca
#Date: Jan 22, 2021
```

## Github
Github repository link is https://github.com/annadlli/STA304-week3tutorial.git
```{r setup, include = FALSE}
library(tidyverse) # A collection of data-related packages
library(janitor) # Helps clean datasets
library(tidyr) # Helps make tidy datasets
library(opendatatoronto)
library(lubridate)
```

## Context about dataset
The dataset is released by the City Clerk's Office for the City of Toronto. It compiles information from 2011-01 to 2021-12 regarding marriage license statistics for Toronto. It compiles data from the 4 Civic Centres located in Scarborough, Etobicoke, North York, and Toronto.

```{r}
#get and clean dataset
dataset <- list_package_resources("e28bc818-43d5-43f7-b5d9-bdfb4eda5feb") |> get_resource()
head(dataset)
cleaned_dataset<- dataset %>% clean_names() |> select(marriage_licenses,time_period) |>
  mutate(time_period = ym(time_period)) |>
  mutate(time_period = as.integer(month(time_period)))
```



```{r}
#Create graph
cleaned_dataset |> group_by(time_period) |>
 summarize(sum = sum(marriage_licenses)) |>
  mutate(time_period = month.abb[time_period]) |>
ggplot(aes(x=time_period, y=sum)) +
geom_col() + 
labs(x="Month",y= "Total number of marriage licenses registered", 
     title ="Torontos' 2011-2021 total number of marriage licenses per month")+
  scale_x_discrete(limits = month.abb)+
  theme_classic()

```

## Citations

R Core Team (2021). R: A language and environment for statistical computing. R Foundation
  for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.

Sharla Gelfand (2020). opendatatoronto: Access the City of Toronto Open Data Portal. R
  package version 0.1.4. https://CRAN.R-project.org/package=opendatatoronto


```{r, include = FALSE}
citation()
citation("opendatatoronto")
```




